### 2021-04-02 Chapter-3/Chapter-3.tex
Updates from Overleaf

Shown in Figure~\ref{fig:side-channel-attack}. We assume a program ($\beta$) has $K$ as its sensitive input. $K$ should be 
a finite set of keys. The program also takes known messages $M$ as its input. 
During an AES encryption, for example, 
$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
some observations ($O$) of the program. Examples of those observations include 
timing, CPU usages, and electromagnetic signals (EM). This paper only
uses secret-dependent control flows and secret-dependent data 
accesses as observations.

@@

\subsection{Secret-dependent Control Transfers}
We think a control-flow is secret-dependent if different input sensitive keys
($K$) can lead to different branch conditions. Therefore,
We define a branch is secret-dependent if:
$$\exists k_{i1}, k_{i2} \in K, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$

>>>>

Shown in Figure~\ref{fig:side-channel-attack}. We assume a program ($\beta$) has $K$ as its sensitive input.  The program also takes public information $M$ as its input. During an AES encryption, for example, 
$\beta$ is the encryption function. $K$ is the set of all possible AES keys, 
and $M$ represents the set consisting of all plaintext messages to be encrypted. In a real execution, an adversary may have 
some observations ($O$) of the program. Examples of those observations include 
timing, CPU usages, and electromagnetic signals (EM). This paper only
uses secret-dependent control flows and secret-dependent data 
accesses as observations.

@@

\subsection{Secret-dependent Control Transfers}
We think a control-flow is secret-dependent if different input sensitive keys
($K$) can lead to different branch conditions. Therefore,
We define a branch is secret-dependent if:
$$\exists k_{i1}, k_{i2} \in K , \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m)$$
